---
title: "Calculations"
date: "Last knitted on `r format(Sys.Date(), '%d %b %Y')`"
author: "Leavitt, Kopf, Weber, Pearson"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console # switch to 'inline' if preferred
---

# Setup

```{r "setup", message = FALSE}
# packages
library(rlang)
library(tidyverse) # general data wrangling and plotting
library(isoprocessor)

# custom funtions
source("scripts/error_propagation.R")
source("scripts/table_functions.R")

# global knitting options for code rendering
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

# Load Data

Applied calibration:

$$
\delta^{2} \text{H}_\text{raw} = \beta_{0} + \beta_{1} \cdot{} \delta^{2} \text{H}_\text{cal} + \beta_{2} \cdot{} A + \beta_{3} \cdot{} \delta^{2} \text{H}_\text{cal} \cdot{} \sqrt{A}
$$

```{r}
# load data
compounds <- readxl::read_excel("data/compounds.xlsx")
organisms <- readxl::read_excel("data/organisms.xlsx")
metadata <- readxl::read_excel("data/metadata.xlsx")
samples <- readxl::read_excel("data/samples.xlsx") 
internal_standard <- readxl::read_excel("data/internal_standard.xlsx") %>%
  mutate(abs_err = abs(calibrated_d2H.permil - true_d2H.permil)) %>%
  arrange(amp2.mV)
# load and save chromatogram in cache
chromatograms <- 
  readxl::read_excel(
    "data/chromatograms.xlsx", 
    col_types = rep(c("numeric", "text", "numeric", "text"), times = c(2, 1, 3, 1))
  )
write_rds(chromatograms, "cache/chromatograms.rds")
```

# Calculations

## Peak-size dependence

Mass balance with a background component:

$$
\begin{aligned}
R_{peak} &= \frac{A_{peak} - A_{bgrd}}{A_{peak}} R_{analyte} + \frac{A_{bgrd}}{A_{peak}} R_{bgrd} \\
\delta_{peak/H2} &= \frac{R_{peak}}{R_{H2}} - 1 \\
  &= \left[ 
    \frac{A_{peak} - A_{bgrd}}{A_{peak}} \frac{R_{analyte}}{R_{VSMOW}} + 
      \frac{A_{bgrd}}{A_{peak}} \frac{R_{bgrd}}{R_{VSMOW}}
    \right] \cdot \frac{R_{VSMOW}}{R_{H2}} - 1 \\
  &= \left[ 
    \frac{A_{peak} - A_{bgrd}}{A_{peak}} \left( \delta_{analyte/VSMOW} + 1 \right) + 
      \frac{A_{bgrd}}{A_{peak}} \left( \delta_{bgrd/VSMOW} + 1 \right)
    \right] \cdot \frac{R_{VSMOW}}{R_{H2}} - 1 \\
  &= \frac{R_{VSMOW}}{R_{H2}} \delta_{analyte/VSMOW} 
  - \frac{R_{VSMOW}}{R_{H2}} \frac{A_{bgrd}}{A_{peak}} \delta_{analyte/VSMOW} 
  +  \frac{R_{VSMOW}}{R_{H2}} \cdot \frac{A_{bgrd}}{A_{peak}} \delta_{bgrd/VSMOW} \\
  &\;\;\;\; + \frac{R_{VSMOW}}{R_{H2}} - 1
\end{aligned}
$$

For individual standard analyses, all peaks have similar amplitudes/areas and we can use a univariate linear regression with $\delta_{analyte/VSMOW}$ as the sole dependent variable to approximate the above equation:

$$
\begin{aligned}
\delta_{peak/H2} &= \beta_1 \cdot \delta_{analyte/VSMOW} + \beta_0
\end{aligned}
$$

with: 

$$
\begin{aligned}
\beta_0 &=  \frac{R_{VSMOW}}{R_{H2}}\frac{A_{bgrd}}{A_{peak}} \delta_{bgrd/VSMOW}  + \frac{R_{VSMOW}}{R_{H2}} - 1 \\
\beta_1 &= \frac{R_{VSMOW}}{R_{H2}}\left(1 - \frac{A_{bgrd}}{A_{peak}} \right)
\end{aligned}
$$

leading to estimates for $\delta_{H2/VSMOW}$ and $\frac{A_{bgrd}}{A_{peak}}$ from the $\beta_0$ and $\beta_1$ equations.

$$
\begin{aligned}

\delta_{H2/VSMOW} &= \frac{1}{R_{VSMOW}/R_{H2}} - 1 = 
  \frac{- \beta_0 + \delta_{bgrd} \cdot (1 - \beta_1) }{1 + \beta_0 + \delta_{bgrd} \cdot \beta_1} 
  \approx \frac{-\beta_0}{1 + \beta_0} \\
\frac{A_{bgrd}}{A_{peak}} &= \frac{1 + \beta_0 - \beta_1}{1 + \beta_0 + \delta_{bgrd} \cdot \beta_1} \approx 1 - \frac{\beta_1}{1 + \beta_0} 
\end{aligned}
$$

```{r}
calc_d2H_vs_VSMOW <- rlang::expr(-value_b0/(1 + value_b0/1000))
calc_percent_bgrd <- rlang::expr(1 - value_b1 / (1 + value_b0/1000))

derived_params <- 
  readxl::read_excel("data/calibration_standards.xlsx") %>%
  filter(calibration == "model.amp") %>%
  group_by(analysis) %>%
  mutate(
    mean_area = mean(area_all.Vs), min_area = min(area_all.Vs), max_area = max(area_all.Vs),
    mean_amp = mean(amp2.mV)/1000, min_amp = min(amp2.mV)/1000, max_amp = max(amp2.mV)/1000
  ) %>%
  ungroup() %>%
  mutate(is_std_peak = TRUE) %>%
  iso_prepare_for_calibration(group_by = analysis) %>%
  iso_generate_calibration(
    # simple direct calibration model
    model = lm(raw_d2H.permil ~ true_d2H.permil), 
    min_n_datapoints = 4
  ) %>%
  # calculate derived parameters
  iso_get_calibration_data(
    select = c(mean_area, min_area, max_area, mean_amp, min_amp, max_amp)
  ) %>%
  iso_get_calibration_parameters(
    select_from_coefs = c(term, estimate, std.error),
    select_from_summary = c()
  ) %>%
  mutate(term = case_when(term == "(Intercept)" ~ "b0", term == "true_d2H.permil" ~ "b1")) %>%
  rename(value = estimate, se = std.error) %>%
  pivot_wider(names_from = term, values_from = c(value, se)) %>%
  mutate(
    `d2H H2/VSMOW [permil]` = !!calc_d2H_vs_VSMOW,
    `d2H H2/VSMOW [permil] error` = propagate_error(!!calc_d2H_vs_VSMOW, dvalue_b0 = se_b0),
    `bgrd / peak` = !!calc_percent_bgrd,
    `bgrd / peak error` = propagate_error(!!calc_percent_bgrd, dvalue_b0 = se_b0, dvalue_b1 = se_b1)
  )

write_rds(derived_params, "cache/derived_params.rds")
```

## Relative abundances

```{r}
# calculate relative abundances for all analyses where all 4 peaks are detected
samples_w_rel_abundances <- 
  samples %>%
  # calculate relative abundances
  group_by(analysis) %>%
  mutate(
    all_phytanes = n() == 4,
    rel_abundance = ifelse(all_phytanes, area_all.Vs / sum(area_all.Vs), NA_real_)
  ) %>%
  ungroup() %>%
  relocate(all_phytanes, rel_abundance, .before = raw_d2H.permil)
```

## Sample error estimates

```{r}
# create estimator for absolute error based on the internal standard
abs_err_model <- loess(
  formula = abs_err ~ amp2.mV,
  data = internal_standard,
  span = 0.75
)
# calculate error estimates
samples_w_analytical_error <- samples_w_rel_abundances %>%
  mutate(
    calibrated_d2H_error.permil = predict(abs_err_model, newdata = tibble(amp2.mV = amp2.mV))
  )
```

## Hydrogenation correction

$$
\delta^{2} \text{H}_\text{cor} = 
  \left(1 + \frac{2}{n_H}\right) \cdot \delta^{2} \text{H}_\text{cal} - 
  \frac{2}{n_H} \cdot \left( (\epsilon^2_\text{hydro} + 1) \cdot (\delta^{2} \text{H}_\text{H2} + 1) - 1 \right)
$$

$$
\sigma_\text{cor} = \sqrt{
  \left(\frac{\partial (\delta^{2} \text{H}_\text{cor})}{\partial  (\delta^{2} \text{H}_\text{cal})} \sigma_\text{cal} \right)^2 + 
  \left(\frac{\partial (\delta^{2} \text{H}_\text{cor})}{\partial  (\delta^{2} \text{H}_\text{H2})} \sigma_\text{H2} \right)^2 +
  \left(\frac{\partial (\delta^{2} \text{H}_\text{cor})}{\partial  (\epsilon^2_\text{hydro})} \sigma_\text{hydro} \right)^2
}
$$

```{r}
# parameters for hydrogenation correction (details in MS)
d2H_H2.permil <- -64 # tank composition
d2H_H2_sd.permil <- 2 # tank composition error
eps_PtO2.permil = -721 # hydrogenation fractionation
eps_PtO2_sd.permil = 152 # hydrogenation fractionation error

# hydrogenation hydrogens
fractionate <- rlang::expr(
  ((d2H_H2.permil/1000 + 1) * (eps_PtO2.permil/1000 + 1) - 1) * 1000
)
hydro_d2H.permil <- eval(fractionate)
hydro_d2H_sd.permil <- propagate_error(!!fractionate, dd2H_H2.permil = d2H_H2_sd.permil, deps_PtO2.permil = eps_PtO2_sd.permil)

# chain lengths of biphytanes
correct_for_H2 <- rlang::expr(
  ((nH + 2) * calibrated_d2H.permil - 2 * hydro_d2H.permil) / nH
)

# calculate corrected d2H
samples_w_hydrogen_correction <- samples_w_analytical_error %>%
  mutate(
    nH = 80 - 2 * parse_number(compound),
    corrected_d2H.permil = !!correct_for_H2,
    corrected_d2H_error.permil = propagate_error(
      !!correct_for_H2, dnH = 0, 
      dcalibrated_d2H.permil = calibrated_d2H_error.permil,
      dhydro_d2H.permil = hydro_d2H_sd.permil
    )
  )

# added uncertainty:
message("Info: values changed by min ", 
        samples_w_hydrogen_correction %>% 
          with(min(corrected_d2H.permil - calibrated_d2H.permil)) %>%
          round(1), "permil")
message("Info: values changed by max ", 
        samples_w_hydrogen_correction %>% 
          with(max(corrected_d2H.permil - calibrated_d2H.permil)) %>%
          round(1), "permil")
message("Info: uncertainty increased by max ", 
        samples_w_hydrogen_correction %>% 
          with(max(corrected_d2H_error.permil - calibrated_d2H_error.permil)) %>%
          round(1), "permil")
```

## Water-lipid fractionation

$$
^{2}\epsilon_\text{L/W} = \frac{\delta^{2} \text{H}_\text{cor} + 1}{\delta^{2} \text{H}_\text{water} + 1} - 1
$$

```{r}
# calculate frationation
fractionate <- rlang::expr(
  ((corrected_d2H.permil/1000 + 1) / (d2H_water.permil/1000 + 1) - 1) * 1000
)
samples_w_epsilons <- samples_w_hydrogen_correction %>%
  left_join(select(metadata, organism, growth, d2H_water.permil), by = c("organism", "growth")) %>%
  mutate(
    eps_2H_lipid_water.permil = !!fractionate,
    eps_2H_lipid_water_error.permil = propagate_error(
      !!fractionate, 
      dcorrected_d2H.permil = corrected_d2H_error.permil,
      dd2H_water.permil = 0.2
    )
  ) %>%
  select(-d2H_water.permil) # for merging of metadata in other Rmds

# save in cache
write_rds(samples_w_epsilons, "cache/samples_w_epsilons.rds")
```

# Data Summaries

## Individual biphytanes

```{r}
# calculate averages of analytical replicates
samples_sum <- samples_w_epsilons %>%
  # calculate number of analyses
  group_by(organism, growth) %>%
  mutate(n_analyses = length(unique(analysis))) %>%
  ungroup() %>%
  # calculate weights
  group_by(organism, compound, growth) %>%
  mutate(
    d2H_norm_weights = 1/corrected_d2H_error.permil^2 / sum(1/corrected_d2H_error.permil^2),
    eps_norm_weights = 1/eps_2H_lipid_water_error.permil^2 / sum(1/eps_2H_lipid_water_error.permil^2),
  ) %>%
  # summarize
  summarize(
    n_analyses = max(n_analyses),
    # unweighted means and sdevs
    d2H_unweighted_mean.permil = mean(corrected_d2H.permil),
    d2H_unweighted_sdev.permil = sd(corrected_d2H.permil),
    eps_unweighted_mean.permil = mean(eps_2H_lipid_water.permil),
    eps_unweighted_sdev.permil = sd(eps_2H_lipid_water.permil),
    # calculate d2H weighted mean
    d2H_weighted_mean.permil = sum(d2H_norm_weights * corrected_d2H.permil),
    # calculate d2H weighted standard deviation
    d2H_weighted_stdev.permil = 
      sqrt(Hmisc::wtd.var(corrected_d2H.permil, 1/corrected_d2H_error.permil^2, normwt = TRUE)),
    # calculate d2H error by standard error propagation
    d2H_propagated_error.permil =
      sqrt(
        sum(
          propagate_error(
            eq = d2H_norm_weights * corrected_d2H.permil,
            dd2H_norm_weights = 0,
            dcorrected_d2H.permil = corrected_d2H_error.permil,
            quiet = TRUE
          )^2
        )
      ),
    # use whichever is larger (d2H_weighted_stdev or d2H_propagated_error)
    d2H_error.permil = ifelse(
      d2H_propagated_error.permil > d2H_weighted_stdev.permil, 
      d2H_propagated_error.permil, d2H_weighted_stdev.permil),
    # calculate eps weighted mean
    eps_weighted_mean.permil = sum(eps_norm_weights * eps_2H_lipid_water.permil),
    # calculate eps weighted standard deviation
    eps_weighted_stdev.permil = 
      sqrt(Hmisc::wtd.var(eps_2H_lipid_water.permil, 1/eps_2H_lipid_water_error.permil^2, normwt = TRUE)),
    # calculate eps error by standard error propagation
    eps_propagated_error.permil =
      sqrt(
        sum(
          propagate_error(
            eq = eps_norm_weights * eps_2H_lipid_water.permil,
            deps_norm_weights = 0,
            deps_2H_lipid_water.permil = eps_2H_lipid_water_error.permil,
            quiet = TRUE
          )^2
        )
      ),
    # use whichever is larger (eps_weighted_stdev or eps_propagated_error)
    eps_error.permil = ifelse(
      eps_propagated_error.permil > eps_weighted_stdev.permil, 
      eps_propagated_error.permil, eps_weighted_stdev.permil),
    # calculate relative abundance mean and error
    rel_abundance_mean = mean(rel_abundance, na.rm = TRUE),
    rel_abundance_error = sd(rel_abundance, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  # clenaup
  select(-ends_with("norm_weights")) %>%
  select(-ends_with("weighted_stdev.permil"), -ends_with("propagated_error.permil")) %>%
  # normalize rel abundance
  group_by(organism, growth) %>%
  mutate(rel_abundance_mean = rel_abundance_mean/sum(rel_abundance_mean)) %>%
  ungroup()

# save in cache
write_rds(samples_sum, "cache/samples_sum.rds")
```

## Ring enrichments

```{r}
# calculate ring difference (for each sample and biphytanes the average difference to all other biphytanes with fewer rings)
ring_enrichments <- samples_sum %>%
  select(organism, compound, growth, eps_weighted_mean.permil, eps_unweighted_mean.permil) %>%
  { full_join(., ., by = c("organism", "growth"))  } %>%
  filter(parse_number(compound.y) > parse_number(compound.x)) %>%
  mutate(
    label = sprintf("BP-%.0f vs. %.0f", parse_number(compound.y), parse_number(compound.x)),
    D_eps_per_ring = (eps_weighted_mean.permil.y - eps_weighted_mean.permil.x)/
      (parse_number(compound.y) - parse_number(compound.x)),
    D_eps_per_ring_unweighted = (eps_unweighted_mean.permil.y - eps_unweighted_mean.permil.x)/
      (parse_number(compound.y) - parse_number(compound.x))
  ) %>%
  rename(compound = compound.y) %>%
  # summarize for each compound
  group_by(organism, growth, compound) %>%
  summarize(
    D_eps_per_ring = mean(D_eps_per_ring),
    D_eps_per_ring_unweighted = mean(D_eps_per_ring_unweighted), 
    .groups = "drop"
  ) %>%
  ungroup()

# mean ring enrichment
message("Mean ring enrichments: ")
ring_enrichments %>% 
  summarize(
    mean_ring_enrichment = mean(D_eps_per_ring) %>% round(1), 
    sd = sd(D_eps_per_ring) %>% round(1),
    mean_ring_enrichment_unweighted = mean(D_eps_per_ring_unweighted) %>% round(1),
    sd_unweighted = sd(D_eps_per_ring_unweighted) %>% round(1),
  )

# save in cache
write_rds(ring_enrichments, "cache/ring_enrichments.rds")
```

## Growth regression

```{r}
growth_regs <- 
  samples_sum %>%
  pivot_longer(
    cols = c(eps_unweighted_mean.permil, eps_weighted_mean.permil),
    names_to = "variable"
  ) %>%
  left_join(metadata, by = c("organism", "growth")) %>%
  nest(data = c(-organism, -variable)) %>%
  mutate(
    fit = map(data, ~lm(value ~ TD.hours, weights = rel_abundance_mean, data = .x)),
    estimates = map(fit, broom::tidy),
    summary = map(fit, broom::glance)
  ) %>%
  unnest(estimates) %>% 
  filter(term == "TD.hours") %>%
  mutate(
    lci = map_dbl(fit, ~confint(.x)["TD.hours", 1]),
    uci = map_dbl(fit, ~confint(.x)["TD.hours", 2])
  ) %>%
  select(1:std.error, lci, uci, summary) %>% 
  unnest(summary)

# save in cache
write_rds(growth_regs, "cache/growth_regs.rds")

# slopes and uncertainty
message("Growth regression: ")
growth_regs %>%
  mutate(
    permil_per_hour = round(estimate, 2), 
    permil_per_hour_err = round(std.error, 2), 
    permil_per_hour_lci = round(lci, 2),
    permil_per_hour_uci = round(uci, 2), 
    permil_per_day = round(estimate * 24, 2), 
    permil_per_day_err = round(std.error * 24, 2),
    r2 = round(adj.r.squared, 2), pval = signif(p.value, 3)
  ) %>%
  select(organism, variable, starts_with("permil_per"), r2, pval)
```


## Abundance weighted biphytanes

```{r}
samples_ab_weighted_sum <- 
  samples_sum %>% 
  group_by(organism, growth) %>%
  summarize(
    d2H_ab_weighted_mean.permil = sum(d2H_weighted_mean.permil * rel_abundance_mean),
    d2H_ab_weighted_mean_error.permil = 
      sqrt(
        sum(
          propagate_error(
            eq = d2H_weighted_mean.permil * rel_abundance_mean,
            dd2H_weighted_mean.permil = d2H_error.permil,
            drel_abundance_mean = rel_abundance_error,
            quiet = TRUE
          )^2
        )
      ),
    eps_ab_weighted_mean.permil = sum(eps_weighted_mean.permil * rel_abundance_mean),
    eps_ab_weighted_mean_error.permil = 
      sqrt(
        sum(
          propagate_error(
            eq = eps_weighted_mean.permil * rel_abundance_mean,
            deps_weighted_mean.permil = eps_error.permil,
            drel_abundance_mean = rel_abundance_error,
            quiet = TRUE
          )^2
        )
      ),
    .groups = "drop"
  )

# save in cache
write_rds(samples_ab_weighted_sum, "cache/samples_ab_weighted_sum.rds")
```

