---
title: "Model"
date: "Last knitted on `r format(Sys.Date(), '%d %b %Y')`"
author: "Rhim, based on the model from Leavitt, Kopf et al. (2023)"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console # switch to 'inline' if preferred
---

# Setup

```{r "setup", message = FALSE}
# packages
library(tidyverse) # general data wrangling and plotting
library(ggpubr)
library(cowplot)
library(dplyr)

# scripts
source("scripts/plotting_functions.R")
source("scripts/error_propagation.R")

# global knitting options for code rendering
knitr::opts_chunk$set(
  eval = TRUE, echo = FALSE,
  collapse = TRUE, comment = "#>",
  dev = c("png", "pdf", "postscript"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("plots", "")
)
```

> NOTE: please knit the `01_calculations.Rmd` notebook first to prepare the data used for plotting.

# Load Data

```{r}
reg_params <- readxl::read_excel("data/model_params_20230523.xlsx", sheet = "reg_fits") %>%
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
reg_params
```

# HETEROTROPHY

```{r}
het_reg_params <- reg_params %>% filter( mode == "heterotrophy")
het_reg_params_TL <- reg_params %>% filter( experiment == "1-TL")
het_reg_params_SL <- reg_params %>% filter( experiment == "2-SL")
R_Lac = -60/1000+1 # will be updated with the actual lactate d2H measurement

het_exp_fractions <- 
  readxl::read_excel("data/model_params_20230523.xlsx", sheet = "het_fvals_exp") %>%
  mutate(across(-c(scenario, scenario_, x, s, total), ~.x/total, .names = "f_{.col}")) %>%  
  mutate(f_W_direct = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS = f_n_Lac_AS) %>%
  mutate(f_Lac = f_S_cofa + f_S_AS)
het_exp_fractions

het_exp_fractions_TL_s0 <-
  het_exp_fractions %>% filter(scenario_ == "s0") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  mutate(f_W_direct_s0 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_s0 = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net_s0 = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa_s0 = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS_s0 = f_n_Lac_AS) %>%
  mutate(f_Lac_s0 = f_S_cofa + f_S_AS) %>%
  mutate(a_W_cofa_s0 = (het_reg_params_TL$estimate_slope - f_W_direct_s0 * (e_W_direct/1000+1)) / (f_W_cofa_s0)) %>%
  mutate(e_W_cofa_s0 = (a_W_cofa_s0 - 1)*1000) 
  het_exp_fractions_TL_s0

het_exp_fractions_TL_s1 <-
  het_exp_fractions %>% filter(scenario_ == "s1") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  crossing(e_S_cofa_s1 = c(-1000, 1000)) %>%

  mutate(f_W_direct_s1 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_s1 = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net_s1 = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa_s1 = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS_s1 = f_n_Lac_AS) %>%
  mutate(f_Lac_s1 = f_S_cofa + f_S_AS_s1) %>%
  mutate(a_W_cofa_s1 = (het_reg_params_TL$estimate_slope - f_W_direct_s1 * (e_W_direct/1000+1)) / (f_W_cofa_s1)) %>%
  mutate(e_W_cofa_s1 = (a_W_cofa_s1 - 1)*1000) %>%
  mutate(a_S_cofa_s1 = e_S_cofa_s1/1000 + 1) %>%
  mutate(a_S_AS_s1 = (het_reg_params_TL$estimate_icept / (R_Lac * f_S_AS_s1)) - (a_S_cofa_s1 * f_S_cofa_s1) / f_S_AS_s1) %>%
  mutate(e_S_AS_s1 = (a_S_AS_s1 - 1)*1000) 

het_exp_fractions_TL_s1

het_exp_fractions_SL_s0 <-
  het_exp_fractions %>% filter(scenario_ == "s0") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  mutate(f_W_direct_s0 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_s0 = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net_s0 = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa_s0 = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS_s0 = f_n_Lac_AS) %>%
  mutate(f_Lac_s0 = f_S_cofa + f_S_AS) %>%
  mutate(a_W_cofa_s0 = (het_reg_params_SL$estimate_slope - f_W_direct_s0 * (e_W_direct/1000+1)) / (f_W_cofa_s0)) %>%
  mutate(e_W_cofa_s0 = (a_W_cofa_s0 - 1)*1000) 
het_exp_fractions_SL_s0

het_exp_fractions_SL_s1 <-
  het_exp_fractions %>% filter(scenario_ == "s1") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  crossing(e_S_cofa_s1 = c(-1000, 1000)) %>%

  mutate(f_W_direct_s1 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_s1 = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net_s1 = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa_s1 = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS_s1 = f_n_Lac_AS) %>%
  mutate(f_Lac_s1 = f_S_cofa_s1 + f_S_AS) %>%
  mutate(a_W_cofa_s1 = (het_reg_params_SL$estimate_slope - f_W_direct_s1 * (e_W_direct/1000+1)) / (f_W_cofa_s1)) %>%
  mutate(e_W_cofa_s1 = (a_W_cofa_s1 - 1)*1000) %>%
  
  mutate(a_S_cofa_s1 = e_S_cofa_s1/1000 + 1) %>%
  mutate(a_S_AS_s1 = (het_reg_params_SL$estimate_icept / (R_Lac * f_S_AS_s1)) - (a_S_cofa_s1 * f_S_cofa_s1) / f_S_AS_s1) %>%
  mutate(e_S_AS_s1 = (a_S_AS_s1 - 1)*1000) 

het_exp_fractions_SL_s1

```

## Model

scenarios:
 - $x = 0$ : no water exchange
 - $x = 1$: water exchange during lipid biosynthesis (note: full water exchange scenario is no longer considered)
 - $s = 0$: no substrate (lactate) contribution
 - $s = 1$: max substrate (lactate) contribution

### hydrogen budget

$$
\begin{aligned}
n_{W_{LS}} &= \frac{2}{3} \cdot (1 - x) \\
n_{W_{GGR}} &= 8 \\
n_{W_{ex}} &= 24 \cdot x \\
n_{W_{direct}} &= n_{W_{LS}} + n_{W_{GGR}} + n_{W_{ex}}\\
~\\
n_{W_{LS,NADPH}} &= 16 \cdot (1 - \frac{1}{3} \cdot s) \\
n_{W_{LS,GGR}} &= 8 \cdot (1 - \frac{1}{3} \cdot s) \\
n_{W_{cofactors}} &= n_{W_{LS,NADPH}} + n_{W_{LS,GGR}}\\
~\\
n_{Lac_{LS,NADPH}} &= 16 \cdot \frac{1}{3} \cdot s \\
n_{Lac_{LS,GGR}} &= 8 \cdot \frac{1}{3} \cdot s \\
n_{Lac_LS} &= n_{Lac_{LS,NADPH}} + n_{Lac_{LS,GGR}}\\
~\\
n_{Lac_{AS}} &= 24 + (23 + 1/3) \cdot (1-x)
\end{aligned}
$$
### mass balance
allowing for some (up to 1/3) portion of NADPH and GGR to come from lactate

$$
\begin{aligned}
R_{BP_{het}} &= f_{W_{net}} \cdot \alpha_{W_{net}} \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
&= (f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}) \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
\end{aligned} \\
~\\
\begin{aligned}
where: &~ f_{W_{direct}} = f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}} \\
&~ f_{W_{cofa}} = f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} \\
&~ f_S = f_{S_{cofa}} + f_{Lac_{AS}} = f_{Lac_{LS_{NADPH}}} + f_{Lac_{LS_{GGR}}} + f_{Lac_{AS}}
\end{aligned}
$$
### regression parameters

$$
\begin{aligned}
m_{het} &= f_{W_{net}} \cdot \alpha_{W_{net}}\\
&= f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}} \\
&=  (f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}}) \cdot \alpha_{W_{direct}} + (f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}}) \cdot \alpha_{W_{cofa}} \\
c_{het} &= f_S \cdot \alpha_S \cdot R_S \\
&= (f_{S_{cofa}} \cdot \alpha_{S_{cofa}} + f_{S_{AS}} \cdot \alpha_{S_{AS}}) \cdot R_S \\

~\\
\alpha_{W_{net}} &= \frac{f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}}{f_{W_{net}}}\\
\end{aligned}
$$
## Calculations

### e_W_cofa vs e_W_direct

```{r}
p1 <- 
  ggplot() +
  
  geom_polygon(aes(x = c(494.171, 494.171, -228.329, -2172.496), y = c(-1000, -1000, 1000, 1000)),
                   fill="#D3C6AB", alpha=0.7) + #s=0
  geom_line(aes(het_exp_fractions_TL_s0$e_W_cofa_s0, het_exp_fractions_TL_s0$e_W_direct, 
                color = het_exp_fractions_TL_s0$scenario), linetype=1, size=1) +
  
  geom_polygon(aes(x = c(1241.2565, 1241.2565, 157.5065, -2758.7435), y = c(-1000, -1000, 1000, 1000)),
                   fill="#79653F", alpha=0.7) + #s=1
  geom_line(aes(het_exp_fractions_TL_s1$e_W_cofa_s1, het_exp_fractions_TL_s1$e_W_direct, 
                color = het_exp_fractions_TL_s1$scenario), linetype=1, size=1) +
  
  scale_color_manual(values = c("#D3C6AB","#79653F","#D3C6AB","#79653F")) +

  geom_hline(yintercept = 0, color ="black", linetype = 3, size=0.7) +
  geom_vline(xintercept = 0, color ="black", linetype = 3, size=0.7) +

  coord_cartesian(xlim = c(-1000, 1000), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_blank(), 
        axis.ticks.length=unit(.25, "cm")) 

p1
```

```{r}
p2 <- 
  ggplot() +
  
  geom_polygon(aes(x = c(636.70967, 636.70967, -85.79033, -2029.95700), y = c(-1000, -1000, 1000, 1000)),
                   fill="#D3C6AB", alpha=0.7) + #s=0
  geom_line(aes(het_exp_fractions_SL_s0$e_W_cofa_s0, het_exp_fractions_SL_s0$e_W_direct, 
                color = het_exp_fractions_SL_s0$scenario), linetype=1, size=1) +
  
  geom_polygon(aes(x = c(1455.0645, 1455.0645, 371.3145, -2544.9355), y = c(-1000, -1000, 1000, 1000)),
                   fill="#79653F", alpha=0.7) + #s=1
  geom_line(aes(het_exp_fractions_SL_s1$e_W_cofa_s1, het_exp_fractions_SL_s1$e_W_direct, 
                color = het_exp_fractions_SL_s1$scenario), linetype=1, size=1) +
  
  scale_color_manual(values = c("#D3C6AB","#79653F","#D3C6AB","#79653F")) +

  geom_hline(yintercept = 0, color ="black", linetype = 3, size=0.7) +
  geom_vline(xintercept = 0, color ="black", linetype = 3, size=0.7) +

  coord_cartesian(xlim = c(-1000, 1000), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_blank(), 
        axis.ticks.length=unit(.25, "cm")) 
p2
```

### e_S_cofa vs e_S_AS

```{r}
p4 <- 
  ggplot() +
  
  annotate("rect", xmin=-1000, xmax=1000, ymin=-453.3, ymax=78.3, # s=0
            fill="#D3C6AB", color="#D3C6AB", alpha=0.7, size=1) +

  geom_polygon(aes(x = c(-1000, -1000, 1000, 1000), y = c(-453.2159, 78.3039, -588.3628, -791.2678)),
                   fill="#79653F", alpha=0.7) + #s=1
  geom_line(aes(het_exp_fractions_TL_s1$e_S_cofa_s1, het_exp_fractions_TL_s1$e_S_AS_s1, 
                color = het_exp_fractions_TL_s1$scenario), linetype=1, size=1) +
  
  scale_color_manual(values = c("#79653F","#79653F")) + 

  geom_hline(yintercept = 0, color ="black", linetype = 3, size=0.7) +
  geom_vline(xintercept = 0, color ="black", linetype = 3, size=0.7) +

  coord_cartesian(xlim = c(-1000, 1000), ylim = c(-1000, 1000), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_blank(), 
        axis.ticks.length=unit(.25, "cm")) 

p4
```

```{r}
p5 <- 
  ggplot() +
  
  annotate("rect", xmin=-1000, xmax=1000, ymin=-547.2, ymax=-107.1, # s=0
            fill="#D3C6AB", color="#D3C6AB", alpha=0.7, size=1) +

  geom_polygon(aes(x = c(-1000, -1000, 1000, 1000), y = c(-547.2056, -107.0518, -773.7184, -885.2576)),
                   fill="#79653F", alpha=0.7) + #s=1
  geom_line(aes(het_exp_fractions_SL_s1$e_S_cofa_s1, het_exp_fractions_SL_s1$e_S_AS_s1, 
                color = het_exp_fractions_SL_s1$scenario), linetype=1, size=1) +
  
  scale_color_manual(values = c("#79653F","#79653F")) +

  geom_hline(yintercept = 0, color ="black", linetype = 3, size=0.7) +
  geom_vline(xintercept = 0, color ="black", linetype = 3, size=0.7) +

  coord_cartesian(xlim = c(-1000, 1000), ylim = c(-1000, 1000), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_blank(), 
        axis.ticks.length=unit(.25, "cm")) 

p5
```

# AUTOTROPHY

```{r}
auto_reg_params <- reg_params %>% filter( mode == "autotrophy")
auto_reg_params

auto_fractions <- 
  readxl::read_excel("data/model_params_20230523.xlsx", sheet = "auto_fvals") %>%
  mutate(across(-c(scenario, scenario_, include, total), ~.x/total, .names = "f_{.col}")) %>%
  mutate(f_W_direct = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_AS = f_n_W_AS_Fd + f_n_W_AS_F420H2) %>%
  mutate(f_W_cofa = f_n_W_LS_NADPH + f_n_W_LS_GGR + f_W_cofa_AS) %>%
  mutate(f_W_net = f_W_direct + f_W_cofa) %>%
  mutate(f_H2 = f_n_H2_AS)
auto_fractions

auto_fractions_s0 <-
  auto_fractions %>% filter(scenario_ == "s0") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  mutate(f_W_direct_s0 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_AS_s0 = f_n_W_AS_Fd + f_n_W_AS_F420H2) %>%
  mutate(f_W_cofa_s0 = f_n_W_LS_NADPH + f_n_W_LS_GGR + f_W_cofa_AS_s0) %>%
  mutate(f_W_net_s0 = f_W_direct + f_W_cofa) %>%
  mutate(f_H2_s0 = f_n_H2_AS) %>%
  mutate(a_W_cofa_s0 = (auto_reg_params$estimate_slope - f_W_direct_s0 * (e_W_direct/1000+1)) / (f_W_cofa_s0)) %>%
  mutate(e_W_cofa_s0 = (a_W_cofa_s0 - 1)*1000) 
auto_fractions_s0

auto_fractions_s1 <-
  auto_fractions %>% filter(scenario_ == "s1") %>%
  crossing(e_W_direct = c(-1000, 1000)) %>%
  mutate(f_W_direct_s1 = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_AS_s1 = f_n_W_AS_Fd + f_n_W_AS_F420H2) %>%
  mutate(f_W_cofa_s1 = f_n_W_LS_NADPH + f_n_W_LS_GGR + f_W_cofa_AS_s1) %>%
  mutate(f_W_net_s1 = f_W_direct + f_W_cofa) %>%
  mutate(f_H2_s1 = f_n_H2_AS) %>%
  mutate(a_W_cofa_s1 = (auto_reg_params$estimate_slope - f_W_direct_s1 * (e_W_direct/1000+1)) / (f_W_cofa_s1)) %>%
  mutate(e_W_cofa_s1 = (a_W_cofa_s1 - 1)*1000) 
auto_fractions_s1

```

## Model

scenarios:
 - $x = 0$ : no water exchange
 - $x = 1$ : water exchange during lipid biosynthesis (note: full water exchange scenario is no longer considered)
 - $s = 0$: no methyl H via Hmd
 - $s = 1$: 1 methyl H via Hmd

### hydrogen budget

$$
\begin{aligned}
n_{W_{LS}} &= \frac{2}{3} \cdot (1 - x) \\
n_{W_{GGR}} &= 8 \\
n_{W_{ex}} &= 24 \cdot x \\
n_{W_{direct}} &= n_{W_{LS}} + n_{W_{GGR}} + n_{W_{ex}}\\
~\\
n_{W_{LS,NADPH}} &= 16\\
n_{W_{LS,GGR}} &= 8\\
n_{W_{AS,Fd_{red}}} &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x))\\
n_{W_{AS,F420H2}} &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x)) \cdot (2-s)\\
n_{W_{cofactors}} &= n_{W_{LS,NADPH}} + n_{W_{LS,GGR}} + n_{W_{AS,Fd_{red}}} + n_{W_{AS,F420H2}}\\
~\\
n_{H2_{AS}}  &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x)) \cdot s\\
\end{aligned}
$$
### mass balance
allowing for some (up to 1/3) portion of acetyl-CoA H's to come from H2 via Hmd

$$
\begin{aligned}
R_{BP_{auto}} &= f_{W_{net}} \cdot \alpha_{W_{net}} \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
&= (f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}) \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
\end{aligned} \\
~\\
\begin{aligned}
where: &~ f_{W_{direct}} = f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}} \\
&~ f_{W_{cofa}} = f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} + f_{W_{AS_{Fd}}} + f_{W_{AS_{F420H2}}} \\
&~ f_S = f_{H2_{AS}}
\end{aligned}
$$
### regression parameters

$$
\begin{aligned}
m_{auto} &= f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}} \\
&=  (f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}}) \cdot \alpha_{W_{direct}} + (f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} + f_{W_{AS_{Fd}}} + f_{W_{AS_{F420H2}}}) \cdot \alpha_{W_{cofa}} \\
c_{het} &= f_S \cdot \alpha_S \cdot R_S \\
&= f_{H2_{AS}} \cdot \alpha_S \cdot R_S
\end{aligned}
$$
## Calculations

### e_W_cofa vs e_W_direct
```{r}
p3 <- 
  ggplot() + 
  
  geom_polygon(aes(x = c(-326.6426140, -569.7040102, -1000, -1000, 0.6523333), 
                   y = c(-1000, 1000, 1000, 500, -1000)),
                   fill="#c0bed7", alpha=0.7) + #s=0
  geom_line(aes(auto_fractions_s0$e_W_cofa_s0, auto_fractions_s0$e_W_direct, 
                color = auto_fractions_s0$scenario), linetype=2, size=1) +
  
  geom_polygon(aes(x = c(-135.3975, -447.4925, -1000, -1000, 200.7828), 
                   y = c(-1000, 1000, 1000, 500, -1000)),
               fill="#7570b3", alpha=0.7) + #s=1
  geom_line(aes(auto_fractions_s1$e_W_cofa_s1, auto_fractions_s1$e_W_direct, 
                color = auto_fractions_s1$scenario), linetype=2, size=1) +
  
  scale_color_manual(values = c("#c0bed7","#7570b3","#c0bed7","#7570b3")) +

  geom_hline(yintercept = 0, color ="black", linetype = 3, size=0.7) +
  geom_vline(xintercept = 0, color ="black", linetype = 3, size=0.7) +

  coord_cartesian(xlim = c(-1000, 1000), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_blank(), 
        axis.ticks.length=unit(.25, "cm")) 

p3
```


# COMBINED PLOTS

```{r}
plot_grid(p3, p1, p2, NULL, p4, p5, nrow=2, ncol=3, align="vh")

```