---
title: "Model"
date: "Last knitted on `r format(Sys.Date(), '%d %b %Y')`"
author: "Rhim, based on the model from Leavitt, Kopf et al. (2023)"
output:
  html_document: 
    df_print: paged
    number_sections: yes
    toc: yes
    toc_float: true
    toc_depth: 3
    code_folding: show
editor_options:
  chunk_output_type: console # switch to 'inline' if preferred
---

# Setup

```{r "setup", message = FALSE}
# packages
library(tidyverse) # general data wrangling and plotting
library(ggpubr)
library(cowplot)
library(dplyr)

# scripts
source("scripts/plotting_functions.R")
source("scripts/error_propagation.R")

# global knitting options for code rendering
knitr::opts_chunk$set(
  eval = TRUE, echo = FALSE,
  collapse = TRUE, comment = "#>",
  dev = c("png", "pdf", "postscript"),
  dev.args = list(pdf = list(encoding = "WinAnsi", useDingbats = FALSE)),
  fig.keep = "all",
  fig.path = file.path("plots", "")
)

# custom funtions
source("scripts/error_propagation.R")
source("scripts/table_functions.R")
```

> NOTE: please knit the `01_calculations.Rmd` notebook first to prepare the data used for plotting.

# Load Data

```{r}
reg_params <- readxl::read_excel("data/model_params_20230820_GrowthPhase.xlsx", sheet = "reg_fits") %>%
  pivot_wider(names_from = term, values_from = c(estimate, std.error, p.value))
reg_params
```

# HETEROTROPHY

```{r}
het_reg_params <- reg_params %>% filter( mode == "heterotrophy")
het_reg_params_TL <- reg_params %>% filter( experiment == "1-TL")
het_reg_params_SL <- reg_params %>% filter( experiment == "2-SL")

het_exp_fractions <- 
  readxl::read_excel("data/model_params_20230820_GrowthPhase.xlsx", sheet = "het_fvals_exp") %>%
  mutate(across(-c(scenario, scenario_, x, s, total), ~.x/total, .names = "f_{.col}")) %>%
  mutate(f_W_direct = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa = f_n_W_LS_NADPH + f_n_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofa) %>%
  mutate(f_S_cofa = f_n_Lac_LS_NADPH + f_n_Lac_LS_GGR) %>%
  mutate(f_S_AS = f_n_Lac_AS) %>%
  mutate(f_Lac = f_S_cofa + f_S_AS)
het_exp_fractions

het_exp_fractions_contXex <-
  readxl::read_excel("data/model_params_20230820_GrowthPhase.xlsx", sheet = "het_fvals_exp_contXex")
het_exp_fractions_contXex

```

## Model

scenarios:
 - $x = 0$ : no water exchange
 - $x = 1$: water exchange during lipid biosynthesis (note: full water exchange scenario is no longer considered)
 - $s = 0$: no substrate (lactate) contribution
 - $s = 1$: max substrate (lactate) contribution

### hydrogen budget

$$
\begin{aligned}
n_{W_{LS}} &= \frac{2}{3} \cdot (1 - x) \\
n_{W_{GGR}} &= 8 \\
n_{W_{ex}} &= 24 \cdot x \\
n_{W_{direct}} &= n_{W_{LS}} + n_{W_{GGR}} + n_{W_{ex}}\\
~\\
n_{W_{LS,NADPH}} &= 16 \cdot (1 - \frac{1}{3} \cdot s) \\
n_{W_{LS,GGR}} &= 8 \cdot (1 - \frac{1}{3} \cdot s) \\
n_{W_{cofactors}} &= n_{W_{LS,NADPH}} + n_{W_{LS,GGR}}\\
~\\
n_{Lac_{LS,NADPH}} &= 16 \cdot \frac{1}{3} \cdot s \\
n_{Lac_{LS,GGR}} &= 8 \cdot \frac{1}{3} \cdot s \\
n_{Lac_LS} &= n_{Lac_{LS,NADPH}} + n_{Lac_{LS,GGR}}\\
~\\
n_{Lac_{AS}} &= 24 + (23 + 1/3) \cdot (1-x)
\end{aligned}
$$
### mass balance
allowing for some (up to 1/3) portion of NADPH and GGR to come from lactate

$$
\begin{aligned}
R_{BP_{het}} &= f_{W_{net}} \cdot \alpha_{W_{net}} \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
&= (f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}) \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
\end{aligned} \\
~\\
\begin{aligned}
where: &~ f_{W_{direct}} = f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}} \\
&~ f_{W_{cofa}} = f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} \\
&~ f_S = f_{S_{cofa}} + f_{Lac_{AS}} = f_{Lac_{LS_{NADPH}}} + f_{Lac_{LS_{GGR}}} + f_{Lac_{AS}}
\end{aligned}
$$
### regression parameters

$$
\begin{aligned}
m_{het} &= f_{W_{net}} \cdot \alpha_{W_{net}}\\
&= f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}} \\
&=  (f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}}) \cdot \alpha_{W_{direct}} + (f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}}) \cdot \alpha_{W_{cofa}} \\
c_{het} &= f_S \cdot \alpha_S \cdot R_S \\
&= (f_{S_{cofa}} \cdot \alpha_{S_{cofa}} + f_{S_{AS}} \cdot \alpha_{S_{AS}}) \cdot R_S \\

~\\
\alpha_{W_{net}} &= \frac{f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}}{f_{W_{net}}}\\
\end{aligned}
$$
## Calculations

### x_ex vs f_W_net
```{r}
p1 <- het_reg_params_TL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  ggplot() +
  geom_polygon(aes(x = c(0, 0, 100, 100), 
                   y = c(0.408*100, 0.308*100, 0.600*100, 0.700*100)),
               fill="#1b9e77", alpha=0.4) +

  geom_line(aes(x_ex*100, f_W_net*100,linetype = scenario), 
            size=1, color="#1b9e77") +
  scale_linetype_manual(values = c(1,2)) +

  coord_cartesian(ylim = c(0, 110), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p1
```

```{r}
p2 <- het_reg_params_SL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  ggplot() +
  geom_polygon(aes(x = c(0, 0, 100, 100), 
                   y = c(0.408*100, 0.308*100, 0.600*100, 0.700*100)),
               fill="#d95f02", alpha=0.4) +

  geom_line(aes(x_ex*100, f_W_net*100,linetype = scenario), 
            size=1, color="#d95f02") +
  scale_linetype_manual(values = c(1,2)) +

  coord_cartesian(ylim = c(0, 110), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p2
```

### x_ex vs eps_W_net 

```{r}
p4 <- het_reg_params_TL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  mutate(a_W_net_exp = estimate_slope_exp / f_W_net) %>%
  mutate(e_W_net_exp = (a_W_net_exp - 1)*1000) %>%
  mutate(e_W_net_exp_se = (std.error_slope_exp / f_W_net) * 1000) %>%
  
  mutate(a_W_net_sta = estimate_slope_sta / f_W_net) %>%
  mutate(e_W_net_sta = (a_W_net_sta - 1)*1000) %>%
  mutate(e_W_net_sta_se = (std.error_slope_sta / f_W_net) * 1000) %>%
  
  ggplot(aes(x_ex*100, e_W_net_exp)) +
  
  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(179-p4$data$e_W_net_exp_se[1],-312-p4$data$e_W_net_exp_se[2],
                         -198+p4$data$e_W_net_exp_se[4],561+p4$data$e_W_net_exp_se[3])),
                   fill="#ace9d7",alpha=0.4) +

  geom_line(aes(x_ex*100, e_W_net_exp, linetype = scenario), size=1, color="#ace9d7") +
  scale_linetype_manual(values = c(1,2)) +


  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(341-p4$data$e_W_net_sta_se[1],-218-p4$data$e_W_net_sta_se[2],
                         -87+p4$data$e_W_net_sta_se[4],776+p4$data$e_W_net_sta_se[3])),
                   fill="#1b9e77",alpha=0.4) +
  geom_line(aes(x_ex*100, e_W_net_sta, linetype = scenario), size=1, color="#1b9e77") +
  scale_linetype_manual(values = c(1,2)) +
  
  coord_cartesian(ylim=c(-500, 0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p4
```

```{r}
p5 <- het_reg_params_SL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR) %>%
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  mutate(a_W_net_exp = estimate_slope_exp / f_W_net) %>%
  mutate(e_W_net_exp = (a_W_net_exp - 1)*1000) %>%
  mutate(e_W_net_exp_se = (std.error_slope_exp / f_W_net) * 1000) %>%
  
  mutate(a_W_net_sta = estimate_slope_sta / f_W_net) %>%
  mutate(e_W_net_sta = (a_W_net_sta - 1)*1000) %>%
  mutate(e_W_net_sta_se = (std.error_slope_sta / f_W_net) * 1000) %>%
  
  ggplot(aes(x_ex*100, e_W_net_exp)) +
  
  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(167-p5$data$e_W_net_exp_se[1],-319-p5$data$e_W_net_exp_se[2],
                         -205+p5$data$e_W_net_exp_se[4],546+p5$data$e_W_net_exp_se[3])),
                   fill="#eac7ac",alpha=0.4) +

  geom_line(aes(x_ex*100, e_W_net_exp, linetype = scenario), size=1, color="#eac7ac") +
  scale_linetype_manual(values = c(1,2)) +


  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(270-p5$data$e_W_net_sta_se[1],-259-p5$data$e_W_net_sta_se[2],
                         -135+p5$data$e_W_net_sta_se[4],682+p5$data$e_W_net_sta_se[3])),
                   fill="#d95f02",alpha=0.4) +
  geom_line(aes(x_ex*100, e_W_net_sta, linetype = scenario), size=1, color="#d95f02") +
  scale_linetype_manual(values = c(1,2)) +

  
  coord_cartesian(ylim=c(-500, 0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p5
```

### x_ex vs eps_S_net
```{r}
R_Lac = -60/1000+1 # will be updated with the actual lactate d2H measurement

p7 <- het_reg_params_TL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_S_LS = f_S_LS_NADPH + f_S_LS_GGR) %>%
  mutate(f_S_AS = (24 + (23 + 1/3) * (1-x_ex))/80) %>%
  mutate(f_Lac = f_S_LS_NADPH + f_S_LS_GGR + f_S_AS) %>%
  
  mutate(a_S_net_exp = estimate_icept_exp / (f_Lac * R_Lac)) %>%
  mutate(e_S_net_exp = (a_S_net_exp - 1)*1000) %>%
  mutate(e_S_net_exp_se = (sqrt((std.error_icept_exp/estimate_icept_exp)^2 + (0.3/-60)^2) * a_S_net_exp * 1000)) %>% # assuming R_Lac_se = 0.3 permil
  
  mutate(a_S_net_sta = estimate_icept_sta / (f_Lac * R_Lac)) %>%
  mutate(e_S_net_sta = (a_S_net_sta - 1)*1000) %>%
  mutate(e_S_net_sta_se = (sqrt((std.error_icept_sta/estimate_icept_sta)^2 + (0.3/-60)^2) * a_S_net_sta * 1000)) %>% # assuming R_Lac_se = 0.3 permil

  ggplot() +
  geom_polygon(aes(x = c(0, 100, 100, 0), 
                   y = c(-511+p07$data$e_S_net_exp_se[1],-35+p07$data$e_S_net_exp_se[2],
                         -277-p07$data$e_S_net_exp_se[4],-582-p07$data$e_S_net_exp_se[3])),
               fill="#ace9d7", alpha=0.4) +
  geom_line(aes(x_ex*100, e_S_net_exp, linetype = scenario), size=1, color="#ace9d7") +
  scale_linetype_manual(values = c(1,2)) +

  geom_polygon(aes(x = c(0, 100, 100, 0), 
                   y = c(-636+p07$data$e_S_net_sta_se[1],-282+p07$data$e_S_net_sta_se[2],
                         -461-p07$data$e_S_net_sta_se[4],-688-p07$data$e_S_net_sta_se[3])),
               fill="#1b9e77", alpha=0.4) +
  geom_line(aes(x_ex*100, e_S_net_sta, linetype = scenario), size=1, color="#1b9e77") +
  scale_linetype_manual(values = c(1,2)) +
  
  coord_cartesian(ylim=c(-500, 0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p7
```

```{r}
R_Lac = -60/1000+1 # will be updated with the actual lactate d2H measurement

p8 <- het_reg_params_SL %>%
  crossing(het_exp_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_S_LS = f_S_LS_NADPH + f_S_LS_GGR) %>%
  mutate(f_S_AS = (24 + (23 + 1/3) * (1-x_ex))/80) %>%
  mutate(f_Lac = f_S_LS_NADPH + f_S_LS_GGR + f_S_AS) %>%
  
  mutate(a_S_net_exp = estimate_icept_exp / (f_Lac * R_Lac)) %>%
  mutate(e_S_net_exp = (a_S_net_exp - 1)*1000) %>%
  mutate(e_S_net_exp_se = (sqrt((std.error_icept_exp/estimate_icept_exp)^2 + (0.3/-60)^2) * a_S_net_exp * 1000)) %>% # assuming R_Lac_se = 0.3 permil
  
  mutate(a_S_net_sta = estimate_icept_sta / (f_Lac * R_Lac)) %>%
  mutate(e_S_net_sta = (a_S_net_sta - 1)*1000) %>%
  mutate(e_S_net_sta_se = (sqrt((std.error_icept_sta/estimate_icept_sta)^2 + (0.3/-60)^2) * a_S_net_sta * 1000)) %>% # assuming R_Lac_se = 0.3 permil

  ggplot() +
  geom_polygon(aes(x = c(0, 100, 100, 0), 
                   y = c(-523+p08$data$e_S_net_exp_se[1],-59+p08$data$e_S_net_exp_se[2],
                         -294-p08$data$e_S_net_exp_se[4],-592-p08$data$e_S_net_exp_se[3])),
               fill="#eac7ac", alpha=0.4) +
  geom_line(aes(x_ex*100, e_S_net_exp, linetype = scenario), size=1, color="#eac7ac") +
  scale_linetype_manual(values = c(1,2)) +

  geom_polygon(aes(x = c(0, 100, 100, 0), 
                   y = c(-594+p08$data$e_S_net_sta_se[1],-201+p08$data$e_S_net_sta_se[2],
                         -401-p08$data$e_S_net_sta_se[4],-653-p08$data$e_S_net_sta_se[3])),
               fill="#d95f02", alpha=0.4) +
  geom_line(aes(x_ex*100, e_S_net_sta, linetype = scenario), size=1, color="#d95f02") +
  scale_linetype_manual(values = c(1,2)) +
  
  coord_cartesian(ylim=c(-500, 0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), #element_blank(), 
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p8
```

# AUTOTROPHY

```{r}
auto_reg_params <- reg_params %>% filter( mode == "autotrophy")
auto_reg_params

auto_fractions <- 
  readxl::read_excel("data/model_params_20230820_GrowthPhase.xlsx", sheet = "auto_fvals") %>%
  mutate(across(-c(scenario, scenario_, include, total), ~.x/total, .names = "f_{.col}")) %>%
  mutate(f_W_direct = f_n_W_LS + f_n_W_GGR + f_n_W_ex) %>%
  mutate(f_W_cofa_AS = f_n_W_AS_Fd + f_n_W_AS_F420H2) %>%
  mutate(f_W_cofa = f_n_W_LS_NADPH + f_n_W_LS_GGR + f_W_cofa_AS) %>%
  mutate(f_W_net = f_W_direct + f_W_cofa) %>%
  mutate(f_H2 = f_n_H2_AS)
auto_fractions

auto_fractions_contXex <-
  readxl::read_excel("data/model_params_20230820_GrowthPhase.xlsx", sheet = "auto_fvals_contXex") 
auto_fractions_contXex

```

## Model

scenarios:
 - $x = 0$ : no water exchange
 - $x = 1$ : water exchange during lipid biosynthesis (note: full water exchange scenario is no longer considered)
 - $s = 0$: no methyl H via Hmd
 - $s = 1$: 1 methyl H via Hmd

### hydrogen budget

$$
\begin{aligned}
n_{W_{LS}} &= \frac{2}{3} \cdot (1 - x) \\
n_{W_{GGR}} &= 8 \\
n_{W_{ex}} &= 24 \cdot x \\
n_{W_{direct}} &= n_{W_{LS}} + n_{W_{GGR}} + n_{W_{ex}}\\
~\\
n_{W_{LS,NADPH}} &= 16\\
n_{W_{LS,GGR}} &= 8\\
n_{W_{AS,Fd_{red}}} &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x))\\
n_{W_{AS,F420H2}} &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x)) \cdot (2-s)\\
n_{W_{cofactors}} &= n_{W_{LS,NADPH}} + n_{W_{LS,GGR}} + n_{W_{AS,Fd_{red}}} + n_{W_{AS,F420H2}}\\
~\\
n_{H2_{AS}}  &= \frac{1}{3} \cdot (24 + (23 + 1/3) \cdot (1-x)) \cdot s\\
\end{aligned}
$$
### mass balance
allowing for some (up to 1/3) portion of acetyl-CoA H's to come from H2 via Hmd

$$
\begin{aligned}
R_{BP_{auto}} &= f_{W_{net}} \cdot \alpha_{W_{net}} \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
&= (f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}}) \cdot R_W + f_S \cdot \alpha_S \cdot R_S \\
\end{aligned} \\
~\\
\begin{aligned}
where: &~ f_{W_{direct}} = f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}} \\
&~ f_{W_{cofa}} = f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} + f_{W_{AS_{Fd}}} + f_{W_{AS_{F420H2}}} \\
&~ f_S = f_{H2_{AS}}
\end{aligned}
$$
### regression parameters

$$
\begin{aligned}
m_{auto} &= f_{W_{direct}} \cdot \alpha_{W_{direct}} + f_{W_{cofa}} \cdot \alpha_{W_{cofa}} \\
&=  (f_{W_{LS}} + f_{W_{GGR}} + f_{W_{ex}}) \cdot \alpha_{W_{direct}} + (f_{W_{LS_{NADPH}}} + f_{W_{LS_{GGR}}} + f_{W_{AS_{Fd}}} + f_{W_{AS_{F420H2}}}) \cdot \alpha_{W_{cofa}} \\
c_{het} &= f_S \cdot \alpha_S \cdot R_S \\
&= f_{H2_{AS}} \cdot \alpha_S \cdot R_S
\end{aligned}
$$
## Calculations

### x_ex vs f_W_net
```{r}
p3 <- auto_reg_params %>%
  crossing(auto_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_AS_Fd = (24+(23+1/3)*(1 - x_ex))/80 * c_W_AS_Fd) %>%
  mutate(f_W_AS_F420H2 = (24+(23+1/3)*(1-x_ex))/80 * c_W_AS_F420H2) %>%
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR + f_W_AS_Fd + f_W_AS_F420H2) %>%
  
  mutate(f_S_AS = (24+(23+1/3)*(1 - x_ex))/80 * c_S_AS) %>%
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  ggplot() +
  geom_polygon(aes(x = c(0, 0, 100, 100), 
                   y = c(1*100, 0.803*100, 0.900*100, 1*100)),
               fill="#7570b3", alpha=0.4) +

  geom_line(aes(x_ex*100, f_W_net*100,linetype = scenario), 
            size=1, color="#7570b3") +
  scale_linetype_manual(values = c(1,2)) +

  coord_cartesian(ylim = c(0, 110), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"),
        axis.title = element_blank(),
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p3
```

### x_ex vs eps_W_net
```{r}
p6 <- auto_reg_params %>%
  crossing(auto_fractions_contXex) %>%
  crossing(x_ex = c(0, 1)) %>%

  mutate(f_W_LS = (2/3 * (1 - x_ex))/80) %>%
  mutate(f_W_GGR = 8/80) %>%
  mutate(f_W_ex = (24 * x_ex)/80) %>%
  mutate(f_W_direct = f_W_LS + f_W_GGR + f_W_ex) %>%
  
  mutate(f_W_AS_Fd = (24+(23+1/3)*(1 - x_ex))/80 * c_W_AS_Fd) %>%
  mutate(f_W_AS_F420H2 = (24+(23+1/3)*(1-x_ex))/80 * c_W_AS_F420H2) %>%
  mutate(f_W_cofactors = f_W_LS_NADPH + f_W_LS_GGR + f_W_AS_Fd + f_W_AS_F420H2) %>%
  
  mutate(f_W_net = f_W_direct + f_W_cofactors) %>%

  mutate(a_W_net_exp = estimate_slope_exp / f_W_net) %>%
  mutate(e_W_net_exp = (a_W_net_exp - 1)*1000) %>%
  mutate(e_W_net_exp_se = (std.error_slope_exp / f_W_net) * 1000) %>%
  
  mutate(a_W_net_sta = estimate_slope_sta / f_W_net) %>%
  mutate(e_W_net_sta = (a_W_net_sta - 1)*1000) %>%
  mutate(e_W_net_sta_se = (std.error_slope_sta / f_W_net) * 1000) %>%
  
  ggplot(aes(x_ex*100, e_W_net_exp)) +
  
  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(-448-p6$data$e_W_net_exp_se[1],-448-p6$data$e_W_net_exp_se[2], 
                         -387+p6$data$e_W_net_exp_se[4],-312+p6$data$e_W_net_exp_se[3])),
                   fill="#c0bed7",alpha=0.4) +

  geom_line(aes(x_ex*100, e_W_net_exp, linetype = scenario), size=1, color="#c0bed7") +
  scale_linetype_manual(values = c(1,2)) +

  geom_polygon(aes(x = c(0,100,100,0), 
                   y = c(-372-p6$data$e_W_net_sta_se[1],-372-p6$data$e_W_net_sta_se[2], 
                         -302+p6$data$e_W_net_sta_se[4],-218+p6$data$e_W_net_sta_se[3])),
                   fill="#7570b3",alpha=0.4) +

  geom_line(aes(x_ex*100, e_W_net_sta, linetype = scenario), size=1, color="#7570b3") +
  scale_linetype_manual(values = c(1,2)) +

  geom_hline(yintercept = -293, color = "grey35", size=0.8, linetype=3) +
  
  coord_cartesian(ylim=c(-500, 0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), 
        axis.title = element_blank(), 
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none",
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25, "cm"))
p6
```

### x_ex vs eps_S_net
```{r}
R_H2 = -296.9/1000+1

p9 <- auto_reg_params %>%
  crossing(auto_fractions_contXex %>% filter(s==100)) %>%
  crossing(x_ex = c(0, 1)) %>%
  
  mutate(f_S_AS = (24+(23+1/3)*(1 - x_ex))/80) %>% # * c_S_AS) %>%
  
  mutate(a_S_net_exp = estimate_icept_exp / (f_S_AS * R_H2)) %>%
  mutate(e_S_net_exp = (a_S_net_exp - 1)*1000) %>%
  mutate(e_S_net_exp_se = (sqrt((std.error_icept_exp/estimate_icept_exp)^2 + (0.3/-296.9)^2) * a_S_net_exp * 1000)) %>% # assuming R_Lac_se = 0.3 permil
  
  mutate(a_S_net_sta = estimate_icept_sta / (f_S_AS * R_H2)) %>%
  mutate(e_S_net_sta = (a_S_net_sta - 1)*1000) %>%
  mutate(e_S_net_sta_se = (sqrt((std.error_icept_sta/estimate_icept_sta)^2 + (0.3/-296.9)^2) * a_S_net_sta * 1000)) %>% # assuming R_Lac_se = 0.3 permil

  ggplot() +
  aes(x_ex*100, e_S_net_exp, color = scenario) + 
  geom_line(aes(x_ex*100, e_S_net_exp),size=1, linetype=2) +
  scale_color_manual(values = c("#c0bed7")) +
  geom_ribbon(aes(ymin = e_S_net_exp - e_S_net_exp_se, ymax = e_S_net_exp + e_S_net_exp_se),fill="#c0bed7", alpha = 0.4, color=NA) +

  aes(x_ex*100, e_S_net_sta, color = scenario) + 
  geom_line(aes(x_ex*100, e_S_net_sta),size=1, linetype=2) +
  scale_color_manual(values = c("#7570b3")) +
  geom_ribbon(aes(ymin = e_S_net_sta - e_S_net_sta_se, ymax = e_S_net_sta + e_S_net_sta_se),fill="#7570b3", alpha = 0.4, color=NA) +

  coord_cartesian(ylim=c(-500,0), expand = FALSE) +

  theme_figure() + 
  theme(aspect.ratio=1, text = element_text(size = 12, color = "black"),
        axis.text = element_text(size = 11, color = "black"), 
        axis.title = element_blank(), 
        plot.subtitle = element_text(size =12, color = "black"),
        legend.position = "none", 
        panel.grid.major = element_line(size=0.6, linetype=3, color="grey85"),
        axis.ticks.length=unit(.25,"cm"))
p9
```

# COMBINED PLOTS

```{r}
plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrow=3, ncol=3, align="vh")
```
